---
title: 'Smell-e Technology: Validating immersive multisensory VR food environments to study food choice'
author: 
  - name: Matti Vuorre
    orcid: 0000-0001-5052-066X
    affiliation: Tilburg University
    affiliation-url: https://www.tilburguniversity.edu/staff/m-j-vuorre
site-url: https://github.com/mvuorre/smell-e
date: now
license: "CC BY"
bibliography: bibliography.bib
format: 
  html:
    theme: zephyr
    toc: true
    toc-depth: 3
    toc-title: Contents
    df-print: kable
    embed-resources: true
  docx: default
title-block-banner: true
title-block-style: default
---

```{r}
#| label: setup
#| include: false
#| cache: false

# Package
library(patchwork)
library(emmeans)
library(scales)
library(cmdstanr)
library(brms)
library(ggbeeswarm)
library(readxl)
library(Hmisc)
library(BSDA)
library(knitr)
library(janitor)
library(tidyverse)

# Document options
knitr::opts_chunk$set(
  echo = knitr::is_html_output(),
  cache = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.height = 2.6,
  fig.width = 7.6,
  dpi = 220
)

# Plotting
theme_set(
  theme_linedraw() +
    theme(panel.grid = element_blank())
)

# Other options
dir.create("models", FALSE)
options(  
  # Table options
  knitr.kable.NA = "",
  digits = 2,
  # HMC and parallel computation options
  brms.backend = Sys.getenv("BRMS_BACKEND", "rstan"), 
  brms.threads = as.integer(Sys.getenv("BRMS_THREADS", 1)),
  mc.cores = as.integer(Sys.getenv("MAX_CORES", 4)),
  # Default contrasts
  contrasts = c(unordered = "contr.treatment", ordered = "contr.poly")
)
ITER <- 5000
```

```{r}
#| label: data-load

# Download the dataset from OSF and then recode the relevant variables.
path <- "data/data.xlsx"
if (!file.exists(path)) {
  dir.create(dirname(path))
  download.file("https://osf.io/download/kwrs6/", path)
}

# Read with clean names
dat <- read_xlsx(path) |> 
  clean_names()

# Rename and label
dat <- dat |> 
  mutate(
    participant_id,
    exposure = factor(
      exposure_mode_uvr_vs_mvr_vs_rl, 
      levels = c("RL", "MVR", "UVR"),
    ),
    stimulus = factor(
      stimuli_type_nf_vs_f,
      levels = c("NF", "F")
    ), 
    gender = factor(
      gender,
      levels = 1:3,
      labels = c("Male", "Female", "Other")
    ),
    volume = salivary_volume,
    craving = subjective_craving_chocolate,
    liking = liking_chocolate,
    presence = presence_average,
    bmi = bmi_kg_m2,
    familiarity_vr,
    trait_g = trait_g_average,
    trait_o = trait_o_average,
    state_i = state_imagery_average,
    .keep = "unused"
  )

# Center covariates
dat <- dat |> 
  mutate(
    across(
      c(familiarity_vr, age, bmi, presence, trait_g, trait_o, state_i), 
      ~as.numeric(scale(., scale = FALSE))
    )
  )

# Exclude people
dat <- filter(
  dat,
  debriefing_check_guessed_study_aim_yes_no == "No"
)
```

# Results

We show the data summaries in @fig-data and @tbl-data.

```{r}
#| label: fig-data
#| fig-cap: Craving (left) and salivary volume (right) means and SEs across the study conditions.

p1 <- dat |> 
  ggplot(aes(exposure, craving, col = stimulus)) +
  scale_y_continuous(
    expand = expansion(c(0.1, .1))
  ) +
  scale_color_brewer(
    "Stimulus",
    palette = "Set1"
  ) +
  stat_summary(
    fun.data = mean_se,
    size = 0.55,
    position = position_dodge(width = .2)
  ) +
  stat_summary(
    fun.y = mean,
    geom = "line",
    aes(group = stimulus),
    linewidth = 0.33,
    position = position_dodge(width = .2)
  ) +
  labs(x = "Exposure", y = "Craving")

p2 <- p1 +
  aes(y = volume) +
  labs(y = "Volume")

p_data <- (p1 | p2) + plot_layout(guides = "collect")
p_data
```

```{r}
#| label: tbl-data
#| tbl-cap: Table of means and SEs.

dat |> 
  pivot_longer(cols = c(craving, volume), names_to = "Outcome") |> 
  summarise(
    mean = mean(value),
    se = sd(value) / sqrt(n()),
    .by = c(Outcome, exposure, stimulus)
  ) |> 
  mutate(
    mean_se = str_glue("{number(mean, .01)} ({number(se, .01)})"), 
    .keep = "unused"
  ) |> 
  pivot_wider(
    names_from = stimulus,
    values_from = mean_se, names_vary = "slowest"
  ) |> 
  kable()
```

## Hypothesis 1

To examine the effects of stimulus type and exposure mode on both psychological and physiological food-cue responses (FCRs), we specified a multilevel regression model that predicted craving (or salivary volume, in a separate model) from stimulus type (food [F] / non-food [NF]), exposure type (real life [RL] / multisensory virtual reality [MVR] / unisensory VR [UVR]), and their interactions both as fixed and random effects across participants. In addition, we specified VR familiarity, sex, age, and self-reported BMI as (centered) covariates as fixed effects. We used the R package brms, with default noninformative prior distributions, for analyses [@bürkner2017; @r2024].

```{r}
#| label: h1-sample
#| output: false

# Estimate the model
fit_craving <- brm(
  craving ~
    stimulus * exposure + familiarity_vr + gender + age + bmi +
    (1 | participant_id),
  dat,
  iter = ITER,
  file = "models/brm-h1-craving"
)

fit_volume <- brm(
  volume ~
    stimulus * exposure + familiarity_vr + gender + age + bmi +
    (1 | participant_id),
  dat,
  iter = ITER,
  file = paste0("models/", "brm-h1-volume")
)

# Function to summarise samples
sm <- function(x, test = "pd", rope_range = c(-0.1, 0.1)) {
  bayestestR::describe_posterior(
    x,
    centrality = "mean",
    dispersion = TRUE,
    test = test,
    rope_ci = 1.0,
    rope_range = rope_range
  ) |> 
    select(-any_of(c("CI", "ROPE_CI", "ROPE_low", "ROPE_high"))) |> 
    mutate(
      # Leave numerics in
      pdn = pd,
      Parameter = str_replace_all(Parameter, "F - NF", "ΔFCR"),
      across(any_of(c("pd", "ROPE_Percentage")), ~percent(., .01))
    ) |> 
    mutate(
      CI = str_glue("[{number(CI_low, .01)}, {number(CI_high, .01)}]"),
      .after = SD
    ) |>
    rename_with(~str_remove(., "_Percentage")) |> 
    tibble()
}
```

We then proceeded to test H1A (ΔFCR [F - NF] > 0), and show the results in @tbl-h1a and @fig-h1a. Given the directional hypothesis, and our plan to use a conventional 5% cutoff, the results showed that food stimuli elicit greater craving in all exposure conditions, but greater salivary volume only in the real life condition.

```{r}
#| label: tbl-h1a
#| tbl-cap: Differences in food-cue responses across exposure conditions. Mean, SD, and CI indicate the posterior mean, standard deviation, and 95% Credible Interval. pd indicates the posterior probability of direction.

emm_h1a_craving <- emmeans(fit_craving, ~stimulus * exposure)
emm_h1a_craving_res <- contrast(
  emm_h1a_craving, "revpairwise", by = "exposure"
) |> 
  sm()
emm_h1a_volume <- emmeans(fit_volume, ~stimulus * exposure)
emm_h1a_volume_res <- contrast(
  emm_h1a_volume, "revpairwise", by = "exposure"
) |> 
  sm()
bind_rows(
  emm_h1a_craving_res,
  emm_h1a_volume_res,
  .id = "Outcome"
) |> 
  mutate(
    Outcome = factor(Outcome, labels = c("Craving", "Volume"))
  ) |> 
  select(-starts_with("CI_"), -pdn) |> 
  kable()
```

```{r}
#| label: fig-h1a
#| fig-cap: Differences in food-cue responses across exposure conditions.

p_h1a <- bind_rows(
  emm_h1a_craving_res,
  emm_h1a_volume_res,
  .id = "Outcome"
) |>
  mutate(
    Outcome = factor(Outcome, labels = c("Craving", "Volume")),
    Parameter = factor(
      Parameter, 
      levels = c("ΔFCR RL", "ΔFCR MVR", "ΔFCR UVR"),
      labels = c("RL", "MVR", "UVR")
    )
  ) |> 
  tibble() |> 
  ggplot(aes(Parameter, Mean, fill = pdn > 0.95)) +
  scale_fill_manual(values = c("white", "black")) +
  scale_y_continuous(
    "ΔFCR"
  ) +
  geom_hline(yintercept = 0, linewidth = 0.2) +
  geom_pointrange(aes(ymin = CI_low, ymax = CI_high), shape = 21) +
  guides(fill = "none") +
  labs(x = "Condition", y = "Estimate") +
  facet_wrap("Outcome", scales = "free")
p_h1a
```

Our second hypothesis (H1B) concerned differences in ΔFCRs between exposure conditions. Specifically, we hypothesized that ΔFCR would be greater in the multisensory VR condition compared to the unisensory VR condition (ΔFCRUVR < ΔFCRMVR). As shown in @tbl-h1b and @fig-h1b, the posterior probability of direction of this quantity did not exceed 95% for either craving or volume. We then turned to our third hypothesis (H1C), asserting that ΔFCR is greater in the real-life condition compared to the unisensory VR condition. @tbl-h1b and @fig-h1b show that this hypothesis was supported for both craving and salivary volume.

```{r}
#| label: tbl-h1b
#| tbl-cap: Differences in food-cue response differences between different exposure conditions.

emm_h1b_craving <- contrast(emm_h1a_craving, "revpairwise", by = "exposure") |> 
  contrast("pairwise", by = NULL) |> 
  sm(
    test = c("pd", "rope"), 
    rope_range = c(-0.1, 0.1) * sd(dat$craving)
  ) |> 
  tibble()
emm_h1b_volume <- contrast(emm_h1a_volume, "revpairwise", by = "exposure") |> 
  contrast("pairwise", by = NULL) |> 
  sm(
    test = c("pd", "rope"), 
    rope_range = c(-0.1, 0.1) * sd(dat$volume)
  ) |> 
  tibble()
bind_rows(
  emm_h1b_craving,
  emm_h1b_volume,
  .id = "Outcome"
) |> 
  mutate(
    Outcome = factor(Outcome, labels = c("Craving", "Volume")),
    Parameter = str_remove_all(Parameter, "ΔFCR "),
    Parameter = str_remove_all(Parameter, "\\("),
    Parameter = str_remove_all(Parameter, "\\)")
  ) |> 
  select(-starts_with("CI_")) |> 
  kable()
```

```{r}
#| label: fig-h1b
#| fig-cap: Differences in food-cue response differences between different exposure conditions.

p_h1b <- bind_rows(
  emm_h1b_craving,
  emm_h1b_volume,
  .id = "Outcome"
) |> 
  mutate(
    Outcome = factor(Outcome, labels = c("Craving", "Volume")),
    Parameter = str_remove_all(Parameter, "\\(ΔFCR "),
    Parameter = str_remove_all(Parameter, "\\)")
  ) |> 
  tibble() |> 
  ggplot(aes(Parameter, Mean, fill = pdn > 0.95)) +
  scale_fill_manual(values = c("white", "black")) +
  scale_y_continuous(
    "ΔFCR"
  ) +
  geom_hline(yintercept = 0, linewidth = 0.2) +
  geom_pointrange(aes(ymin = CI_low, ymax = CI_high), shape = 21) +
  guides(fill = "none") +
  labs(x = "Condition", y = "Estimate") +
  facet_wrap("Outcome", scales = "free")

p_h1b <- p_h1b +
  geom_hline(
    data = tibble(
      Outcome = c("Craving", "Volume"),
      rope_low = -0.1 * c(sd(dat$craving), sd(dat$volume)),
      rope_high = 0.1 * c(sd(dat$craving), sd(dat$volume))
    ),
    aes(yintercept = rope_low),
    linetype = "dashed", linewidth = 0.25
  ) +
    geom_hline(
    data = tibble(
      Outcome = c("Craving", "Volume"),
      rope_low = -0.1 * c(sd(dat$craving), sd(dat$volume)),
      rope_high = 0.1 * c(sd(dat$craving), sd(dat$volume))
    ),
    aes(yintercept = rope_high),
    linetype = "dashed", linewidth = 0.25
  )

p_h1b
```

We then hypothesized that the difference between food vs non-food FCR is equal in the multisensory VR condition and real life conditions would be equal. To test this, we decided to treat ΔFCRs within 0.1 standard deviations of the respective FCR as equivalent. Then we calculated the proportion of the respective posterior distribution within that interval to ascertain confidence in the equivalence statement. We labelled these as ROPE_Percentage in @tbl-h1b. These posterior probabilities of equivalence were small (craving: 1%; volume: 45%) and we therefore did not find support for H1D.

```{r}
#| label: fig-h1
#| fig-cap: Combined figure of H1 results

p_h1b <- p_h1b + 
  scale_x_discrete(labels = ~str_replace(.x, " - ", " -\n"))

(p_h1a | p_h1b) +
  plot_annotation(tag_levels = "A")
```

## Hypothesis 2

```{r}
#| label: fig-dag
#| fig-height: 1.4
#| fig-width: 1.6
#| fig-cap: "Schematic of the proposed mediation model. E: Exposure, P: Presence, FCR: Food cue response."

library(dagitty)
g <- dagitty("dag{ 
  E -> P -> FCR ;
  E -> FCR ;
 }")
coordinates(g) <- list(
  x = c(E = 0, P = 1, FCR = 2),
  y = c(E = 0, P = -0.1, FCR = 0)
)
plot(g)
```

We then turned to examine the potential psychological processes that might mediate the effects of VR exposure on food cue responses. We first calculated mean FCRs for each exposure mode (across stimuli), because presence (potential mediator) was only measured once per exposure mode. We then specified a multivariate regression model predicting presence from VR exposure mode (UVR / MVR), and one predicting FCR from presence and all predictors as in the previous model. We specified both paths with by-person random intercepts. We then quantified whether presence mediates FCR effects of the multisensory VR condition by multiplying the VR exposure mode (unisensory VR vs multisensory VR) -> presence path coefficient with the presence -> FCR path coefficient.

```{r}
#| label: h2-sample
#| output: false

# Data for exploratory state imagery mediation
# it is rated on every trial
dat_e1 <- dat |> 
  filter(exposure != "RL") |> 
  mutate(exposure = factor(exposure, levels = c("UVR", "MVR"))) |> 
  select(
    participant_id, stimulus, exposure, 
    craving, volume, presence, state_i,
    familiarity_vr, gender, age, bmi
  )

# Data for H2, presence is rated once per exposure mode
# so we ensure data is not duplicated due to including both stimuli
dat_h2 <- dat_e1 |> 
  summarise(
    across(c(craving, volume), mean),
    .by = c(participant_id, exposure, presence, familiarity_vr:bmi)
  )

c1 <- bf(
  presence ~ exposure + (1 |p| participant_id)
)
c2 <- bf(
  craving ~
    exposure + familiarity_vr + gender + age + bmi + presence +
    (1 |p| participant_id)
)

fit_craving_h2 <- brm(
  c1 + c2 + set_rescor(FALSE),
  dat_h2,
  iter = ITER,
  file = paste0("models/", "brm-h2-craving"), 
  control = list(adapt_delta = 0.99),
  file_refit = "on_change"
)

v2 <- bf(
  volume ~
    exposure + familiarity_vr + gender + age + bmi + presence +
    (1 |p| participant_id)
)
fit_volume_h2 <- brm(
  c1 + v2 + set_rescor(FALSE),
  dat_h2,
  iter = ITER,
  file = paste0("models/", "brm-h2-volume"),
  control = list(adapt_delta = 0.99),
  file_refit = "on_change"
)
```

We show the results in @tbl-h2 and @fig-h2: While the multisensory VR exposure led to greater feelings of presence (path E->P), presence did not credibly predict either craving or salivary volume FCR (P->FCR), and thus the indirect effect were not credibly different from zero (E->P * P->FCR path; Proportion mediated).

```{r}
#| label: tbl-h2
#| tbl-cap: Results of mediation models.

hypotheses_craving <- c(
  `E->P` = "presence_exposureMVR = 0",
  `P->FCR` = "craving_presence = 0",
  `E->P * P->FCR` = "presence_exposureMVR * craving_presence = 0",
  Prop_mediated = "(presence_exposureMVR * craving_presence) / 
    (presence_exposureMVR * craving_presence + craving_exposureMVR) = 0"
)

h_craving <- hypothesis(
  fit_craving_h2,
  hypotheses_craving
)

hypotheses_volume <- hypotheses_craving |> 
  str_replace_all("craving", "volume") |> 
  set_names(h_craving$hypothesis$Hypothesis)

h_volume <- hypothesis(
  fit_volume_h2,
  hypotheses_volume
)

bind_rows(
  h_craving$samples |> 
    set_names(h_craving$hypothesis$Hypothesis) |> 
    sm(),
  h_volume$samples |> 
    set_names(h_volume$hypothesis$Hypothesis) |> 
    sm() |> 
    slice(-1), # The E->P path is not unique to outcome
  .id = "Outcome"
) |> 
  mutate(Outcome = factor(Outcome, labels = c("Craving", "Volume"))) |> 
  select(-starts_with("CI_"), -pdn) |> 
  kable()
```

```{r}
#| label: fig-h2
#| fig.cap: Mediation analyses.

cc1 <- conditional_effects(
  fit_craving_h2,
  "exposure",
  resp = "presence",
  robust = FALSE
)

cc2 <- conditional_effects(
  fit_craving_h2,
  "presence",
  resp = "craving",
  robust = FALSE
)

cc3 <- conditional_effects(
  fit_volume_h2,
  "presence",
  resp = "volume",
  robust = FALSE
)

p1 <- plot(
  cc1, 
  plot = FALSE,
  cat_args = list(size = 3)
  )[[1]] +
  labs(x = "Exposure", y = "Presence") |
  plot(
    cc2, 
    plot = FALSE,
    line_args = list(color = "black", linewidth = 0.5)
  )[[1]] +
  labs(x = "Presence", y = "FCR [Craving]") |
  plot(
    cc3, 
    plot = FALSE,
    line_args = list(color = "black", linewidth = 0.5)
  )[[1]] +
  labs(x = "Presence", y = "FCR [Volume]")
p1 + plot_layout(widths = c(2, 4, 4))
```

## Exploratory analyses

### State imagery

We then turned to our more exploratory analyses. Our first aim was to examine whether state gustatory mental imagery might mediate any effects of VR exposure mode on FCRs. To do so, we conducted mediation analyses as above (Hypothesis 2) but used imagery as the mediator rather than presence. (Consequently, no aggregation was necessary because imagery was rated after each trial.) We show the results in @tbl-e1 and @fig-e1: While the multisensory VR exposure led to elevated imagery, imagery credibly predicted only craving (and thus the indirect path of exposure mode on craving via imagery was credibly nonzero) but not salivary volume FCR.

```{r}
#| label: e1-sample
#| output: false

c1 <- bf(
  state_i ~ exposure + (1 |p| participant_id)
)
c2 <- bf(
  craving ~
    exposure + familiarity_vr + gender + age + bmi + state_i +
    (1 |p| participant_id)
)

fit_craving_e1 <- brm(
  c1 + c2 + set_rescor(FALSE),
  dat_e1,
  iter = ITER,
  file = paste0("models/", "brm-craving-e1"),
  control = list(adapt_delta = 0.99),
  file_refit = "on_change"
)

v2 <- bf(
  volume ~
    exposure + familiarity_vr + gender + age + bmi + state_i +
    (1 |p| participant_id)
)
fit_volume_e1 <- brm(
  c1 + v2 + set_rescor(FALSE),
  dat_e1,
  iter = ITER,
  file = paste0("models/", "brm-volume-e1"),
    control = list(adapt_delta = 0.99),
  file_refit = "on_change"
)
```

```{r}
#| label: tbl-e1
#| tbl-cap: State imagery results.

hypotheses_craving <- c(
  `E->I` = "statei_exposureMVR = 0",
  `I->FCR` = "craving_state_i = 0",
  `E->I * I->FCR` = "statei_exposureMVR * craving_state_i = 0",
  Prop_mediated = "(statei_exposureMVR * craving_state_i) / 
    (statei_exposureMVR * craving_state_i + craving_exposureMVR) = 0"
)

h_craving <- hypothesis(
  fit_craving_e1,
  hypotheses_craving
)

hypotheses_volume <- hypotheses_craving |> 
  str_replace_all("craving", "volume") |> 
  set_names(h_craving$hypothesis$Hypothesis)

h_volume <- hypothesis(
  fit_volume_e1,
  hypotheses_volume
)

bind_rows(
  h_craving$samples |> 
    set_names(h_craving$hypothesis$Hypothesis) |> 
    sm(),
  h_volume$samples |> 
    set_names(h_volume$hypothesis$Hypothesis) |> 
    sm() |> 
    slice(-1), # The E->P path is not unique to outcome
  .id = "Outcome"
) |> 
  mutate(Outcome = factor(Outcome, labels = c("Craving", "Volume"))) |>
  select(-starts_with("CI_"), -pdn) |> 
  kable()
```

```{r}
#| label: fig-e1
#| fig-cap: State imagery results.

cc1 <- conditional_effects(
  fit_craving_e1,
  "exposure",
  resp = "statei",
  robust = FALSE
)

cc2 <- conditional_effects(
  fit_craving_e1,
  "state_i",
  resp = "craving",
  robust = FALSE
)

cc3 <- conditional_effects(
  fit_volume_e1,
  "state_i",
  resp = "volume",
  robust = FALSE
)

p1 <- plot(
  cc1, 
  plot = FALSE,
  line_args = list(color = "black", linewidth = 0.5)
)[[1]] +
  labs(x = "Exposure", y = "State imagery") |
  plot(
    cc2, 
    plot = FALSE, 
    line_args = list(color = "black", linewidth = 0.5)
  )[[1]] +
  labs(x = "State imagery", y = "FCR [Craving]") |
  plot(
    cc3, 
    plot = FALSE,
    line_args = list(color = "black", linewidth = 0.5)
  )[[1]] +
  labs(x = "State imagery", y = "FCR [Volume]")

p1 + plot_layout(widths = c(2, 4, 4))
```

### Trait imagery

We then examined whether individuals' trait gustatory or olfactory imagery moderated any exposure effects on FCRs. To do so, we expanded the models from H1 to include the main effects of gustatory and olfactory imagery (in separate models) and their interactions with stimulus, exposure, and their interaction. As is shown in @tbl-e2, the three-way interactions between stimulus, exposure, and either gustatory or olfactory imagery were not credible different from zero.

```{r}
#| label: e2-sample
#| output: false

fit_craving_e2g <- brm(
  craving ~
    stimulus * exposure * trait_g + familiarity_vr + gender + age + bmi +
    (1 | participant_id),
  dat,
  iter = ITER,
  file = paste0("models/", "brm-craving-e2g")
)
fit_craving_e2o <- brm(
  craving ~
    stimulus * exposure * trait_o + familiarity_vr + gender + age + bmi +
    (1 | participant_id),
  dat,
  iter = ITER,
  file = paste0("models/", "brm-craving-e2o")
)

fit_volume_e2g <- brm(
  volume ~
    stimulus * exposure * trait_g + familiarity_vr + gender + age + bmi +
    (1 | participant_id),
  dat,
  iter = ITER,
  file = paste0("models/", "brm-volume-e2g")
)
fit_volume_e2o <- brm(
  volume ~
    stimulus * exposure * trait_o + familiarity_vr + gender + age + bmi +
    (1 | participant_id),
  dat,
  iter = ITER,
  file = paste0("models/", "brm-volume-e2o")
)
```


```{r}
#| label: tbl-e2
#| tbl-cap: Trait imagery results.

tibble(
  Outcome = rep(c("Craving", "Volume"), each = 2),
  Imagery = rep(c("Gustatory", "Olfactory"), 2),
  model = list(
    fit_craving_e2g, fit_craving_e2o, 
    fit_volume_e2g, fit_volume_e2o
  )
) |> 
  mutate(res = map(model, ~sm(.x) |> tail(2) |> select(-Rhat, -ESS))) |> 
  select(-model) |> 
  unnest(res) |> 
  mutate(
    Parameter = str_replace(Parameter, "b_stimulusF", "Food"),
    Parameter = str_remove(Parameter, "exposure")
  ) |> 
  select(-starts_with("CI_"), -pdn) |> 
  kable()
```

# Appendix

## Debriefing Checks

```{r}
#| label: debriefing-check
#| error: true

tmp <- dat |> 
  distinct(participant_id, debriefing_check_guessed_study_aim_yes_no) |> 
  pull(debriefing_check_guessed_study_aim_yes_no) |> 
  table()
binom.test(rev(tmp))
```

The proportion of individuals with "Yes" in `debriefing_check_guessed_study_aim_yes_no` was 0.29.

## Manipulation Checks

```{r}
#| label: manip-check-1

tmp <- dat |> 
  summarise(
    hunger = mean(hunger),
    craving = mean(craving),
    liking = mean(liking),
    .by = participant_id
  )
z.test(tmp$hunger, mu = 50, sigma.x = sd(tmp$hunger))
```

Mean hunger was not significantly different from 50.

```{r}
#| label: manip-check-2

z.test(tmp$craving, mu = 62.95, sigma.x = sd(tmp$craving))
```

Mean craving was significantly less than 62.95.

```{r}
#| label: manip-check-3

z.test(tmp$liking, mu = 50, sigma.x = sd(tmp$liking))
```

Mean liking was significantly greater than 50.

# References

# Computational environment {.appendix}

```{r}
#| label: session-info

sessionInfo()
```
